---
geometry: margin=1in
link-citations: yes
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/ecology.csl
bibliography: library.bib
fontsize: 12pt
font-famliy: "Times New Roman"
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    template: rmd_template.tex
    fig_caption: yes
    keep_tex: yes
    toc: no
    number_sections: no
    includes:
        in_header: format.sty
    pandoc_args:
      - "--filter"
      - "pandoc-crossref"
  bookdown::word_document2:
    fig_width: 6
    fig_caption: yes
    reference_docx: rmd_style.docx
    pandoc_args:
    - "--filter"
    - "pandoc-crossref"
    - "--mathml"
---


```{r caching, include=FALSE}
library(methods)
library(knitr)
library(kableExtra)
library(png)
library(grid)
library(pander)
source("rmd_func.r")
```


**Title: Title of your manuscript**

$$ $$

First Author^1,2^ Second Author^2^, and Third Author^3^

$$ $$

^1^ First Affiliation

^2^ Second Affiliation

^3^ Third Affiliation


`r page_break("Abstract")`

Your abstract.

# Introduction

Your introduction [@Wright2004a].
Some more text [@Kraft2008].
More text [@Hubbell2001].

# Material and Methods

Your Material and Methods. We fitted XXXX:

\begin{equation}
N_{ij} \sim NB(\mu_{ij}, \phi)
(\#eq:NB)
\end{equation}

where $\mu_{ij}$ is xxxxxx, xxxxxxxx,

\begin{equation}
\mu_{ij} \times v_i = exp(\Sigma \beta_{jk} z_{ik})
(\#eq:mu)
\end{equation}

where $\beta_{jk}$ is xxxxxx. Prior for $\phi$ in Eq. \@ref(eq:NB) was specified as xxxxx.

We found XXX (Fig. \@ref(fig:scatplt) and Table \@ref(tab:tblm)). 
We also found xxx (Fig. \@ref(fig:boxplt)) yay! 

# Discussion

Some texts.

# References

<div id="refs"></div>


`r page_break()`


Table: (\#tab:tblm). Summary of the regression model.

```{r tblm, echo = FALSE}
fit <- lm(mpg ~ wt * cyl, data = mtcars)
tb1 <- pander(fit, caption = "")
tb1
```

`r page_break()`

```{r tblm2, echo = FALSE}
tb2 <- head(mtcars)
kable(tb2, caption = "Some datasets.")

```

`r page_break("Figures")`

```{r scatplt, echo = F, dpi = 300, fig.width = 5, fig.height = 5, fig.cap = "Scatter plot of XXX. Each point indicates XXXX."}

img <- readPNG("images/scat.png", native = TRUE, info = TRUE)
grid.raster(img, interpolate=F)

```

`r page_break()`

```{r boxplt, echo = F, dpi = 300, fig.width = 5, fig.height = 5, fig.cap = "Boxplot of XXXX."}

img <- readPNG("images/boxp.png", native = TRUE, info = TRUE)
grid.raster(img, interpolate=F)

```
